For finitary induction-Induction, Induction is Enough

### 2020-04-13 paper/paper.tex
example: infinitary Pi

The theory of signatures in \cite{Kaposi:2019:CQI:3302515.3290315} is a small
type theory in which every context encodes a valid quotient inductive-inductive
type (QIIT) signature. For example, the signature for natural numbers is simply
the context $(Nat:\U,zero:Nat,suc:Nat\ra Nat)$ of length three ($Nat$, $zero$
and $suc$ are variable names). \cite{Kaposi:2019:CQI:3302515.3290315} showed
that if this theory of signatures exists, then any finitary QIIT can be derived
from it via a term model construction.
Here, by finitary QIIT, we mean that infinitary constructors, such as the following
one, are not allowed:
\[ TODO \]
If we omit the type former for equality
constructors from the theory of signatures, we get a theory of finitary IIT
signatures, and the construction of \cite{Kaposi:2019:CQI:3302515.3290315} still
works: constructing an arbitrary IIT from the theory of IIT signatures does not
need the $\mathsf{Id}$ type former to be present.

>>>>

The theory of signatures in \cite{Kaposi:2019:CQI:3302515.3290315} is a small
type theory in which every context encodes a valid quotient inductive-inductive
type (QIIT) signature. For example, the signature for natural numbers is simply
the context $(Nat:\U,zero:Nat,suc:Nat\ra Nat)$ of length three ($Nat$, $zero$
and $suc$ are variable names). \cite{Kaposi:2019:CQI:3302515.3290315} showed
that if this theory of signatures exists, then any finitary QIIT can be derived
from it via a term model construction.
Here, by finitary QIIT, we mean that infinitary constructors, such as the following
infinitary $\Pi$, are not allowed:
\[
  \Pi_\infty : (\Gamma : \Con) \rightarrow (\mathbb{N} \rightarrow \Ty\,\Gamma) \rightarrow \Ty\,\Gamma
   \]
If we omit the type former for equality
constructors from the theory of signatures, we get a theory of finitary IIT
signatures, and the construction of \cite{Kaposi:2019:CQI:3302515.3290315} still
works: constructing an arbitrary IIT from the theory of IIT signatures does not
need the $\mathsf{Id}$ type former to be present.
